Binary companions of evolved stars in \apogee\ \DR: \\ Search method and catalog of $\sim$5,000 companions

### 2018-04-03 paper/1-catalog/twoface-catalog.tex
Marla

It is a pleasure to thank
Kevin Covey (WWU),
Marina Kounkel (WWU),
Keith Hawkins (Columbia),
Melissa Ness (Columbia/Flatiron),
David Spergel (Princeton/Flatiron),
and Yuan-Sen Ting (Princeton).

>>>>

It is a pleasure to thank
Kevin Covey (WWU),
Marla Geha (Yale),
Marina Kounkel (WWU),
Keith Hawkins (Columbia),
Melissa Ness (Columbia/Flatiron),
David Spergel (Princeton/Flatiron),
and Yuan-Sen Ting (Princeton).
